PK object batch mode trial

### 2023-08-10 data-raw/batchMode_trial_gpm.Rmd
Updating summary method and finalizing the testing vignette.

@@

@@

mvbutils::foodweb(where = asNamespace("invivoPKfit"),
                  prune = "bp_test",
                  border = TRUE, cex = 1, lwd = 1.5)

@@

fun_mat2 %>%
  as_tibble(rownames = NA) %>%
  rownames_to_column(var = "from") %>%
  pivot_longer(cols = !from,
               names_to = "to",
               values_to = "Call") %>%
  filter(Call != 0) %>% 
  transmute(
    from = str_remove(from, pattern = ".pk"),
    to = str_remove(to, pattern = ".pk")
  ) %>%
  filter(from %in% c("residuals"),
         !(to %in% c("check_model",
                     "check_method",
                     "check_newdata",
                     "check_required_status"))) %>%
  ggflowchart::ggflowchart(horizontal = TRUE)
```

>>>>

# easy fit
my_predata <- cvt %>%
  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% "DTXSID5020732")

@@

my_pk <- do_preprocess(my_pk)
plot(my_pk, print_out = TRUE)

@@

mvbutils::foodweb(where = asNamespace("invivoPKfit"),
                  prune = "compare_models",
                  border = TRUE, cex = 1, lwd = 1.5)

@@

fun_mat2 %>%
  as_tibble(rownames = NA) %>%
  rownames_to_column(var = "from") %>%
  pivot_longer(cols = !from,
               names_to = "to",
               values_to = "Call") %>%
  filter(Call != 0) %>% 
  transmute(
    from = str_remove(from, pattern = ".pk"),
    to = str_remove(to, pattern = ".pk")
  ) %>%
  filter(from %in% c("residuals"),
         !(to %in% c("check_model",
                     "check_method",
                     "check_newdata",
                     "check_required_status"))) %>%
  ggflowchart::ggflowchart(horizontal = TRUE)

# Random Bits
# 
rmse(my_pk) %>%
  group_by(!!!my_pk$data_group, model, method, Route, Media, Dose) %>%
  mutate(avg_rmse = mean(RMSE)) %>%
  nest(full_rmse = c(Time, RMSE))

fold_errors(my_pk) %>%
  group_by(!!!my_pk$data_group, model, method, Route, Media, Dose) %>%
  mutate(avg_FoldErr = mean(Fold_Error),
         median_FoldErr = median(Fold_Error),
         within_2fold = sum(Fold_Error >= 0.5 & Fold_Error <= 2)/length(Fold_Error)) %>%
  dplyr::select(Time, Fold_Error, avg_FoldErr, median_FoldErr, within_2fold) %>%
  nest(full_fold_errors = c(Time, Fold_Error))
